Karbowski model in 2-D

### 2020-05-19 paper/supplementary/supp.tex
Adds text based on realization that Bard's suggestion can't be implemented as suggested#

in the style of the preprint.

Although I have re-implemented rd\_james\_comp2, which expresses
Eq.~\ref{eq:J_NM_with_comp},and found that it does provide competition enough
to generate a barrel field like ordering, I've not yet implemented Bard's
suggestion precisely, so I think that's up next. However, I imagine that this
may be unstable without the sigmoiding of $a_i$ in the expression for
$\chi_i$.

>>>>

in the style of the preprint. There's a problem here. The problem is that the
gradient of $\hat{a}_i$ is a \emph{vector} quantity. So in fact, Bard's
suggestion doesn't make good sense, and Eq.~\ref{eq:J_NM_with_comp} is more
sensible.

I have re-implemented rd\_james\_comp2, which expresses
Eq.~\ref{eq:J_NM_with_comp}, and found that it does provide competition enough
to generate a barrel-field-like ordering.
